A Fredholm operator approach to the plate buckling problem

### 2018-08-16 doc/draft-01/08append.tex
Adding mathematica notebook and appending appendix for estimate on  radiaiton condition

>>>>

\begin{lem}
If $\bu = \nabla^{\perp} H_{0}(\omega r)$ and $p\to 0$ as $r\to \infty$, 
then
\begin{equation}
\lim_{r\to \inf} \sqrt(r) \left(\ff_{1} - i\omega \bu_{1} \right) = 0 \, .
\end{equation}
\end{lem}

\begin{proof}
If $\bu = \nabla^{\perp} H_{0}(\omega r) = (\partial_{y} H_{0}(\omega r), 
-\partial_{x} H_{0}(\omega r))$, then
\begin{equation}
\nabla  p = (\Delta + \omega^2) \bu = (\Delta + \omega^2) \nabla^{\perp} 
H_{0} (\omega r) = 0 \, .
\end{equation}
Since $p\to 0$ as $r\to \infty$, we conclude that $p=0$.
\begin{align}
\ff_{1} &= 2\partial_{x} u_{1} \cos(\theta) + \left( \partial_{x} u_{2} + 
\partial_{y} u_{1} \right) \sin(\theta) \\
&= 2 \partial_{xy} H_{0}(\omega r) \cdot \frac{x}{r} +
\left[-\partial_{xx} H_{0}(\omega r) + \partial_{yy} H_{0}(\omega r) \right]
\cdot \frac{y}{r} \, .
\end{align}
Based on the mathematica script (radcond1.nb in our mathematica folder), we
get
\begin{equation}
\ff_{1} - i \omega u_{1} = \frac{ky}{r^2} \left( -kr \left(H_{0}(\omega r) + 
i H_{1}(\omega r)\right) +
2 H_{1}(\omega r)\right) \, .
\end{equation}
The result then follows from the asymptotic properties of Hankel functions since
\begin{equation}
H_{0}(z) = c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
\text{and} \quad 
H_{1}(z) = i \cdot c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
\end{equation}
where $c$ is the same constant in both of these expansions.
\end{proof}
